asc_file_database

### 2019-03-27 src/stack_test.Rmd
stuff

need tidyr package
```{r}

unlayer <- read.csv("../data/env/asc_layerlist1998.csv", header = TRUE)
unlayer <- subset(unlayer, ascmonths == 1)
unlayer <- unlayer[-c(1), ]
unlayer[] <- lapply(unlayer, as.character) #from https://stackoverflow.com/questions/2851015/convert-data-frame-columns-from-factors-to-characters
aea <- raster("../output/env/aea.tif")

for (td in 1:nrow(unlayer)){
  temp_depth <- raster(unlayer$temp_depth[td])
  #crs(temp_depth) <- +proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0 
  names(temp_depth) <- "temp_depth"
  #temp_depth <- projectRaster(temp_depth, aea)
  chl_surface <- raster(unlayer$chl_surface[td])
  names(chl_surface) <- "chl_surface"
  o2_depth <- raster(unlayer$o2_depth[td])
  names(o2_depth) <- "o2_depth"
  salinity_depth <- raster(unlayer$salinity_depth[td])
  names(salinity_depth) <- "salinity_depth"
  nao_sample <- raster(unlayer$nao_sample[td])
  names(nao_sample) <- "nao_sample"
  nao_winter <- raster(unlayer$nao_winter[td])
  names(nao_winter) <- "nao_winter"
  stackn <- unlayer$stackname[td]
  test <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)
  #stackSave(test,unlayer$stackname[td])
  pred <- predict(mod1, test, file = paste0("../output/maxentpredict/", stackn), overwrite=TRUE) 
  preplot <- plot(pred, png(paste0("../output/maxentpredict/", stackn, ".png")))
  paste("maxplot_", stackn, ".png", sep = "") # to automatically save the plot to a png AND show it inline

}
dev.off() # stops automatic saving of the plot to a png
# now call the stack...

@@

mod1 <- maxent(x = prab, p = pa, path = paste0("../output/maxentout"), args =  c("responsecurves"), save(md, file = "../output/maxentmod"))

@@

for (td in 1:nrow(unlayer)){
  temp_depth <- raster(unlayer$temp_depth[td])
  crs(temp_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(temp_depth) <- "temp_depth"
  temp_depth <- projectRaster(temp_depth, aea)
  chl_surface <- raster(unlayer$chl_surface[td])
  crs(chl_surface) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(chl_surface) <- "chl_surface"
  chl_surface <- projectRaster(chl_surface, aea)
  o2_depth <- raster(unlayer$o2_depth[td])
  crs(o2_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(o2_depth) <- "o2_depth"
  o2_depth <- projectRaster(o2_depth, aea)
  salinity_depth <- raster(unlayer$salinity_depth[td])
  crs(salinity_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(salinity_depth) <- "salinity_depth"
  salinity_depth <- projectRaster(salinity_depth, aea)
  nao_sample <- raster(unlayer$nao_sample[td])
  crs(nao_sample) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(nao_sample) <- "nao_sample"
  nao_sample <- projectRaster(nao_sample, aea)
  nao_winter <- raster(unlayer$nao_winter[td])
  crs(nao_winter) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
  names(nao_winter) <- "nao_winter"
  nao_winter <- projectRaster(nao_winter, aea)
  stackn <- unlayer$stackname[td]
  test <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)
  #stackSave(test,unlayer$stackname[td])
  pred <- predict(mod1, test, file = paste0("../output/maxentpredict/", stackn, ".asc"), overwrite=TRUE) #sam you just added.asc but have not tested
  paste("maxplot_", stackn, ".png", sep = "") # to automatically save the plot to a png AND show it inline
  preplot <- plot(pred, png(paste0("../output/maxentpredict/", stackn, ".png")))
  dev.off() # stops automatic saving of the plot to a png
}

@@

#-----------------------
strt <- Sys.time() #get the start time
mod7 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4")) #threads should speed things up...
mod7

@@

mod8.1 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "betamultiplier=0.25")) #playing with multiplier
mod8.1

@@

mod8 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4")) #default setting for betam is 1
mod8

@@

mod8.4 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "betamultiplier=1.25")) #playing with multiplier
mod8.4

@@

mod8.2 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "betamultiplier=2")) 
mod8.2

@@

mod8.3 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "betamultiplier=6")) 
mod8.3

@@

#play with test and training data - note will want to give your own file in the 'real model'
mod9 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30")) 
mod9

@@

mod10 <- maxent(x = subpresaball, p = subpaall, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30")) 
mod10

@@

mod11 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "replicates=10")) #replicates added
mod11

@@

mod12 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "addsamplestobackground=TRUE")) #add to samples because field study with biased data - see https://esajournals.onlinelibrary.wiley.com/doi/10.1890/10-1171.1. note this should be the default but keep here as a note
mod12

@@

mod1all <- maxent(x = janpresaball, p = paall, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4")) 
mod1all

@@

betamval <- 0.25
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=0.25"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 0.50
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=0.50"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 0.75
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=0.75"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 1
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=1"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 1.25
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=1.25"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 1.50
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=1.50"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 1.75
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=1.75"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 2
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=2"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 2.25
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=2.25"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 2.50
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=2.50"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 2.75
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=2.75"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 3
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=3"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 3.25
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=3.25"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 3.50
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=3.50"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 3.75
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=3.75"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 4
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=4", "randomtestpoints=30", "betamultiplier=4"), path = "../output/maxent/output/mod9foraic")

@@

>>>>

@@

@@

for (td in 1:nrow(unlayer)){
  temp_depth <- raster(unlayer$temp_depth[td])
  crs(temp_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(temp_depth) <- "temp_depth"
  temp_depth <- projectRaster(temp_depth, aea)
  chl_surface <- raster(unlayer$chl_surface[td])
  crs(chl_surface) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(chl_surface) <- "chl_surface"
  chl_surface <- projectRaster(chl_surface, aea)
  o2_depth <- raster(unlayer$o2_depth[td])
  crs(o2_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(o2_depth) <- "o2_depth"
  o2_depth <- projectRaster(o2_depth, aea)
  salinity_depth <- raster(unlayer$salinity_depth[td])
  crs(salinity_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(salinity_depth) <- "salinity_depth"
  salinity_depth <- projectRaster(salinity_depth, aea)
  nao_sample <- raster(unlayer$nao_sample[td])
  crs(nao_sample) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(nao_sample) <- "nao_sample"
  nao_sample <- projectRaster(nao_sample, aea)
  nao_winter <- raster(unlayer$nao_winter[td])
  crs(nao_winter) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
  names(nao_winter) <- "nao_winter"
  nao_winter <- projectRaster(nao_winter, aea)
  stackn <- unlayer$stackname[td]
  test <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)
  #stackSave(test,unlayer$stackname[td])
  pred <- predict(mod1, test, file = paste0("../output/maxentpredict/", stackn, ".asc"), overwrite=FALSE) 
  paste("maxplot_", stackn, ".png", sep = "") # to automatically save the plot to a png AND show it inline
  #preplot <- plot(pred, png(paste0("../output/maxentpredict/", stackn, ".png"))) #keep these out if using xvalidation
  #dev.off() # stops automatic saving of the plot to a png #keep these out if using xvalidation
}

@@

#-----------------------
strt <- Sys.time() #get the start time
mod7 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8")) #threads should speed things up...
mod7

@@

mod8.1 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "betamultiplier=0.25")) #playing with multiplier
mod8.1

@@

mod8 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8")) #default setting for betam is 1
mod8

@@

mod8.4 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "betamultiplier=1.25")) #playing with multiplier
mod8.4

@@

mod8.2 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "betamultiplier=2")) 
mod8.2

@@

mod8.3 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "betamultiplier=6")) 
mod8.3

@@

#play with test and training data - note will want to give your own file in the 'real model'
mod9 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "randomtestpoints=30")) 
mod9

@@

mod10 <- maxent(x = subpresaball, p = subpaall, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "randomtestpoints=30")) 
mod10

@@

mod11 <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "replicates=10")) #replicates added
mod11

@@

mod12 <- maxent(x = prab, p = pa, file = .asc, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "addsamplestobackground=TRUE", "replicatetype=crossvalidate", "replicates=5")) #add to samples because field study with biased data - see https://esajournals.onlinelibrary.wiley.com/doi/10.1890/10-1171.1. note this should be the default but keep here as a note
mod12

mod12[2]

@@

mod1all <- maxent(x = janpresaball, p = paall, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8")) 
mod1all

@@

betamval <- 0.25
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "randomtestpoints=30", "betamultiplier=0.25"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 0.50
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "randomtestpoints=30", "betamultiplier=0.50"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 0.75
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "randomtestpoints=30", "betamultiplier=0.75"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 1
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "randomtestpoints=30", "betamultiplier=1"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 1.25
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "randomtestpoints=30", "betamultiplier=1.25"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 1.50
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "randomtestpoints=30", "betamultiplier=1.50"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 1.75
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "randomtestpoints=30", "betamultiplier=1.75"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 2
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "randomtestpoints=30", "betamultiplier=2"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 2.25
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "randomtestpoints=30", "betamultiplier=2.25"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 2.50
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "randomtestpoints=30", "betamultiplier=2.50"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 2.75
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "randomtestpoints=30", "betamultiplier=2.75"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 3
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "randomtestpoints=30", "betamultiplier=3"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 3.25
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "randomtestpoints=30", "betamultiplier=3.25"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 3.50
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "randomtestpoints=30", "betamultiplier=3.50"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 3.75
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "randomtestpoints=30", "betamultiplier=3.75"), path = "../output/maxent/output/mod9foraic")

@@

betamval <- 4
modaic <- maxent(x = prab, p = pa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "randomtestpoints=30", "betamultiplier=4"), path = "../output/maxent/output/mod9foraic")

@@

#subset background points

```{r}
# now loop to create stacks
janpres <- read.csv("../output/bio/maxenttestjanpr.csv", header = TRUE)
janpres$occ <- 1
janab <- read.csv("../output/bio/maxenttestjanab.csv", header = TRUE)
janab$occ <- 0

#subset2500 randomly
janab25 <- sample_n(janab, 2500)

prab <- rbind(janpres, janab25)
prab$originalscientificname <- "cap" #because species name needs to be the same
pa <- prab$occ
prab <- subset(prab, select = -c(x, y, occ, originalscientificname)) #ok so for maxent in r just need the variables

mod13 <- maxent(x = prab, p = pa, file = .asc, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "addsamplestobackground=TRUE"))

for (td in 1:nrow(unlayer)){
  temp_depth <- raster(unlayer$temp_depth[td])
  crs(temp_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(temp_depth) <- "temp_depth"
  temp_depth <- projectRaster(temp_depth, aea)
  chl_surface <- raster(unlayer$chl_surface[td])
  crs(chl_surface) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(chl_surface) <- "chl_surface"
  chl_surface <- projectRaster(chl_surface, aea)
  o2_depth <- raster(unlayer$o2_depth[td])
  crs(o2_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(o2_depth) <- "o2_depth"
  o2_depth <- projectRaster(o2_depth, aea)
  salinity_depth <- raster(unlayer$salinity_depth[td])
  crs(salinity_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(salinity_depth) <- "salinity_depth"
  salinity_depth <- projectRaster(salinity_depth, aea)
  nao_sample <- raster(unlayer$nao_sample[td])
  crs(nao_sample) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(nao_sample) <- "nao_sample"
  nao_sample <- projectRaster(nao_sample, aea)
  nao_winter <- raster(unlayer$nao_winter[td])
  crs(nao_winter) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
  names(nao_winter) <- "nao_winter"
  nao_winter <- projectRaster(nao_winter, aea)
  stackn <- unlayer$stackname[td]
  test <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)
  #stackSave(test,unlayer$stackname[td])
  pred <- predict(mod13, test, file = paste0("../output/maxentpredict/", stackn, ".asc"), overwrite=FALSE) 
  paste("maxplot_", stackn, ".png", sep = "") # to automatically save the plot to a png AND show it inline
  #preplot <- plot(pred, png(paste0("../output/maxentpredict/", stackn, ".png"))) #keep these out if using xvalidation
  #dev.off() # stops automatic saving of the plot to a png #keep these out if using xvalidation
}
```
